---
title: "Data Preparation"
output: html_document
---

```{r}
require(Rfacebook)
require(wordVectors)
require(feather)
require(stringr)
```


```{r}
df <- read.csv("https://raw.githubusercontent.com/BuzzFeedNews/2016-10-facebook-fact-check/master/data/facebook-fact-check.csv")
names(df)

token <- "EAACEdEose0cBAJwDGZCeOdhvBeZCZB64xZBWUQFToxqkMJvwsEXDULShoR9d6WdZBza7nur3tFaGVG6SdJMeT0XITqXOHjb59bmueZBLbXYqrQtEaqxf8XM6BST948lANLddSVAxcZBXWZAZCgv5BQDXvs2IRYD7VrrZAWDR1tIhi5EYFtcq1WI4rrmjKoesLOlgoZD"

me <- getUsers("me", token=token)
```

#Collecting posts from Facebook API
```{r}
df$post_id <- paste(df$account_id,'_',df$post_id, sep = "")

#removing dysfunctional post ids
df<- df[-c(1128,1326,2201),]


post <- c()

for(i in 1:nrow(df))
{
  post <- c(post, getPost(df$post_id[i], token = token, n = 1000, likes = TRUE, comments = TRUE))
}

```

#Collecting Comments and cleaning the file 
```{r}
for (i in 1:nrow(df))
{
  comments <- c(comments, sapply(post[i*3]$comments[3], function(x) gettext(post[i*3]$comments[3])))
}

comments <- gsub("[^[:alnum:][:blank:]+?&/\\-]", "", comments)
corpus <- Corpus(VectorSource(comments))

inspect(corpus[500])
commentFB <- tm_map(corpus, removePunctuation)
commentFB <- tm_map(commentFB, removeWords, c(stopwords("english"), "http.*"))
commentFB <- tm_map(commentFB, content_transformer(tolower))
commentFB <- tm_map(commentFB, removeNumbers)
commentFB <- tm_map(commentFB, stripWhitespace)


lapply(comments, write, "commentsClean.txt", append=TRUE)
```

#Training the vectors using word2vec skip-grams model on the entire comments corpus
```{r}
trainComment <- train_word2vec("CommentsClean.txt", output_file = "train1.bin",vector=300)
```


#Taking only comments present in the final dataset
```{r}
comments1<- comments[as.numeric(rownames(final))]
```

#Getting vectors for comments
```{r, cache=T}
v <- c()
 for( i in 1: length(comments1))
 {
  x <-  as.vector(strsplit(comments1[i]," +"))
  a <- c()
  for( j in 1:length(x[[1]]))
  {  
           a <- rbind(a,trainComments1[[ x[[1]][j] ]] )
    
  }
  d <- colMeans(a,na.rm = T)
  
  v <- rbind(v, d)
}
   
```

#Getting post messages from post list elements
```{r}
#1 , 4, 7, 
#str(post)
post_mess <- data.frame()
post_message<- data.frame()
j = 1 
for (i in 1:length(post))
{
    if(i ==1 ){
    post_message[j,1] <-   post[[i]][1]
     post_message[j,2] <-  post[[i]][3]
    rbind(post_mess, post_message)
    j = j + 1
    }

  else{
    if ( i %% 3 == 1){
      post_message[j,1] <-  post[[i]][1]
      post_message[j,2]  <- post[[i]][3]
       rbind(post_mess, post_message)
       j = j+ 1
    }
  }
}


```



#Getting  vectors for post message and storing in a matrix named r 
```{r}
 r <- c()
 for( i in 1: nrow(post_message))
 {
  x <-  as.vector(strsplit(post_message$message[i]," +"))
  a <- c()
  for( j in 1:length(x[[1]]))
  {  
           a <- rbind(a,trainComments[[ x[[1]][j] ]] )
    
  }
  d <- colMeans(a,na.rm = T)
 
  
  r <- rbind(r, d)
}
```

#adding post vectors to the finaldataset
```{r}
 f <- as.data.frame(r)
finalDataset[,13:312] <- f[,1:300]
finalDataset <- na.omit(finalDataset)
```


#Taking relevant columns
```{r}
dataset <- subset(finalDataset, select = -c(account_id, Category, Page, Post.URL,Date.Published))
#dataset$Rating <- as.factor(dataset$Rating)
#dataset$Debate <- as.factor(dataset$Debate)
names(dataset)  
str(dataset)
```




The original dataset has an imbalanced no of reponse categorical variables

Response factors notation
mix 1
no factual  content : 4
mostly true 3
mostly false 2 

We shall prepare a new datset for analyis which shall contain a balance of mostly true(~67 %) and mostly  false (~33 % ) response variables.
```{r}
#converting to factors
dataset$Rating <- as.factor(as.numeric(dataset$Rating))
str(dataset$Rating)

#Removing mix and no factual content and reassigning factors: true = 1 and false = 0 
dataset1 <- dataset[dataset$Rating!=1 ,]
dataset1 <- dataset1[dataset1$Rating!=4 ,]
dataset1$Rating <- as.numeric(gsub(3, 1, dataset1$Rating))
dataset1$Rating <- as.numeric(gsub(2, 0, dataset1$Rating))

dataset1$Rating <- as.factor(dataset1$Rating)

true <- dataset1[dataset1$Rating == 1,]
false <- dataset1[dataset1$Rating == 0,]

final <- rbind(true[1:192,], false)

#assigning 0 for no debate(empty cells) and 1 for debate
final$Debate <- gsub("yes",1 ,final$Debate)
final$Debate <- gsub(" ","" ,final$Debate)
final$Debate <- gsub("",0 ,final$Debate)
final$Debate <- gsub(0101,1 ,final$Debate)
```


#Taking only comments present in the final dataset
```{r}
comments1<- comments[as.numeric(rownames(final))]
```

#Getting vectors for comments
```{r, cache=T}
comments_vec <- c()
 for( i in 1: length(comments1))
 {
  x <-  as.vector(strsplit(comments1[i]," +"))
  a <- c()
  for( j in 1:length(x[[1]]))
  {  
           a <- rbind(a,trainComments[[ x[[1]][j] ]] )
    
  }
  d <- colMeans(a,na.rm = T)
  
  comments_vec <- rbind(comments_vec, d)
}
   
```
